Local Spectral Clustering of Density Upper Level Sets

### 2019-05-24 neurips/local_spectral_density_clustering_arxiv.tex
supplement -> appendix

The proof of Theorem \ref{thm: misclassification_rate}, along with all other
proofs in this paper, is deferred to the supplementary material. Note that this 
result says the symmetric set difference metric \smash{$\Delta(\Csig[\Xbf],
  \Cest)$} is proportional to the difficulty of the clustering problem, as
measured by the condition number $\kappa(\Cset)$.

@@

\paragraph{Approximate PPR vector.}  In practice, exactly solving \eqref{eqn:
  ppr_vector} may be too computationally expensive. To address this limitation,
\citet{andersen2006} introduced the \emph{$\epsilon$-approximate} PPR vector
(aPPR), which we will denote by \smash{$\pbf^{(\epsilon)}$}. We refer the
curious reader to \citet{andersen2006} for a formal algorithmic definition of
the aPPR vector, and limit ourselves to highlighting a few salient points: the
aPPR vector can be computed in order $\mathcal{O}(1/(\epsilon\alpha))$ time,
while satisfying the following uniform error bound: 
\begin{equation}
\label{eqn: appr_error}
\textrm{for all $u \in V$}, \quad \pbf(u) - \epsilon \Dbf_{uu}\leq
\pbf^{(\epsilon)}(u) \leq \pbf(u).  
\end{equation}
Application of \eqref{eqn: appr_error} within the proofs of Theorems \ref{thm:
  misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}
leads to analogous results which hold for \smash{$\pbf^{(\epsilon)}$}. We
formally state and prove this in the supplement.

@@

We provide numerical experiments to investigate the tightness of our bounds on
the normalized cut and mixing time of $\Csig[\Xbf]$, and examine the performance
of PPR on the ``two moons'' dataset. For space reasons, we defer details of the
experimental settings to the supplement.

>>>>

The proof of Theorem \ref{thm: misclassification_rate}, along with all other
proofs in this paper, is deferred to the appendix. Note that this 
result says the symmetric set difference metric \smash{$\Delta(\Csig[\Xbf],
  \Cest)$} is proportional to the difficulty of the clustering problem, as
measured by the condition number $\kappa(\Cset)$.

@@

\paragraph{Approximate PPR vector.}  In practice, exactly solving \eqref{eqn:
  ppr_vector} may be too computationally expensive. To address this limitation,
\citet{andersen2006} introduced the \emph{$\epsilon$-approximate} PPR vector
(aPPR), which we will denote by \smash{$\pbf^{(\epsilon)}$}. We refer the
curious reader to \citet{andersen2006} for a formal algorithmic definition of
the aPPR vector, and limit ourselves to highlighting a few salient points: the
aPPR vector can be computed in order $\mathcal{O}(1/(\epsilon\alpha))$ time,
while satisfying the following uniform error bound: 
\begin{equation}
\label{eqn: appr_error}
\textrm{for all $u \in V$}, \quad \pbf(u) - \epsilon \Dbf_{uu}\leq
\pbf^{(\epsilon)}(u) \leq \pbf(u).  
\end{equation}
Application of \eqref{eqn: appr_error} within the proofs of Theorems \ref{thm:
  misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}
leads to analogous results which hold for \smash{$\pbf^{(\epsilon)}$}. We
formally state and prove this in the appendix.

@@

We provide numerical experiments to investigate the tightness of our bounds on
the normalized cut and mixing time of $\Csig[\Xbf]$, and examine the performance
of PPR on the ``two moons'' dataset. We defer details of the experimental
settings to the appendix.
